%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\usepackage{enumitem}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

% \lastupdated % Print the Last Updated text at the top right

\namesection{Haoda}{Li}{ % Your name
\href{mailto:haoda.li@mail.utoronto.ca}{haoda.li@mail.utoronto.ca} | 306 987 2666 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page


%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\location{Computer Vision}
Pytorch/torchvision \textbullet{} Tensorflow \\
OpenCV\textbullet{} Scikit-image\\
Multimedia\textbullet{}3D Vision\\
\subsectionspace

\location{Computer Graphics}
WebGL(OpenGL)\textbullet{}CUDA\\
Geometry Processing\textbullet\\
Physcics Based Animation\\
\subsectionspace

\location{Machine Learning/Data Science}
Pandas\textbullet{}Plotly\textbullet{}SciPy\textbullet{}\\
Pytorch\textbullet{}Tensorflow\textbullet{}Scikit\\
SQL\textbullet{}MongoDB\textbullet{}AWS/Google Cloud\\
\subsectionspace

\location{Web Full Stack}
React \& React Native\textbullet{}TypeScript\\
Django\textbullet{}Go\textbullet{}NodeJS\\
Database (SQL/NoSQL)\textbullet{}AWS\textbullet{}GCP\\
Linux\textbullet{}Bash\textbullet{}Docker
\subsectionspace

\location{Programming Languages}
Python \textbullet{} JavaScript \textbullet{} C++ \textbullet{} Java \\ 
C \textbullet{}Go\textbullet{} Matlab \textbullet{} R\\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------
\section{Awards} 
\descript{Dr. James A. \& Connie P. Dickson Scholarship In Science \& Mathematics}
\location{2020 Sept.| Toronto, ON}
\subsectionspace
\descript{University College Special Admission Scholarships}
\location{2017 Sept. | Toronto, ON}
\subsectionspace
\descript{Provincial Champion, Hypatia Mathematics Contest}
\location{2014 Apr. | Waterloo, ON}
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------

\section{Organizations} 


\descript{Web Manager}
\location{Aug.2019-Present}
University of Toronto\\
Anime, Comics, and Games Club\\
\subsectionspace
\descript{Software Developer} 
\location{Mar. 2018 - Sept. 2018}
Team Wealthy Piggy\\
University of Toronto Hatchery



\sectionspace % Some whitespace after the section


\section{Links} 
\href{https://lihd1003.github.io/}{lihd1003.github.io}\\
\href{https://github.com/lihd1003}{github.com/lihd1003} \\
\href{https://www.linkedin.com/in/haoda-li-515b26165/}{linkedin.com/in/haoda-li-515b26165} \\

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------
\section{Summary}
A fourth year computer science and data science student who is passionate in integrating new computer vision and multimedia technologies and developing cool applications.

\section{Education} 

\subsection{University of Toronto St. George Campus}
\location{Sept.2017 - Present | Toronto, ON}
\descript{Honours Bachelor of Science}
Specialist in Computer Science and Data Science\\
GPA: 3.89/4.0 Dean's List (All Semesters) \\

\section{Experience}

\runsubsection{Huawei Canada}
\descript{| Research Engineer Intern}
\location{May 2020 - Present | Markham, ON}
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Worked in \textbf{Noah's Ark Lab Canada, Compute Vision team}.
\item Assisted the fellow researchers on developing cutting edge methods on video event localization and content understanding.
\item Developed a large scaled (>500 classes) video segmentation and labelling system, which have been integrated to the company's production pipeline.
\item Researched and integrated various cutting edge CV and multimedia technologies to develop the AI engine for video editing applications. 
\end{itemize}


\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Easy Group Inc.}
\descript{| Full Stack Developer}
\location{May 2019 – Apr. 2020 | Toronto, ON}
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
\item Designed and created the user account (database) system which features automatic customer analysis and sales prediction. Currently, the system manages >240,000 users.
\item Worked on creating the customer relation management system to unify the customer information hold by different subsidiaries.
\item Created and managed the 4 subsidiaries' brand websites and 7 online shops.
\end{itemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Research
%------------------------------------------------

\section{Research}

\runsubsection{Wang Lab, Vector Institute}
\descript{| Undergrad Researcher}

\location{Sept. 2019 – Apr. 2020 | Toronto, ON}
Supervised by \textbf{Prof. Bo Wang}, created \textbf{SCAWP}, a web application which allows biomedical researchers to easily pre-process, analyze, and interact with single cell data. The application contains a modern interface for easily building data processing pipelines and a library for 3D interactive data visualizations. 

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Dept. of Economics, U of Toronto}
\descript{| Research Assistant}

\location{Apr. 2019 – Aug. 2019 | Toronto, ON}
Assisted \textbf{Prof. Luo Yao}'s research on the characteristic predictions of hotel tax evasions among Airbnb hosts in Texas. Collected, cleaned, and analyzed hotel tax data, Airbnb's sales data, and hotels sales data. Assisted on implementing the analysis algorithm and creating interactive map for visualizing region and seasonality changes of taxation. 

\sectionspace % Some whitespace after the section


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}